---
title: "Staph metagenome coverage analysis"
author: "Tim Read"
date: "August 13, 2015"
output: html_document
---
```{r}
print(date())
```

This workflow combines binstrain and coverage data from our Staph metagenome analysis and produces useful plots.  Also save data tables filtered at two different coverage levels for subsequent analysis in other workflows.
###Libraries
```{r}
library(googlesheets)
library("dplyr")
library(assertthat)
library(gtools)
source('./staph_metagenome_tools.R')
```

###Download the coverage data from googlesheets

```{r, echo=FALSE}
covs <- gs_title("Coverage_Staph_MeCA") # note: might need to register app with google here .
print(covs$updated)
mapping <-gs_read(covs)
```

###Import the binstrain data, merge, clean and harmonize colnames
```{r}
dat3 <- read.csv("./Data/Final_HMP_Matrix.csv", header = TRUE, stringsAsFactors = FALSE)
dat3 <- dat3[,-(2:5)] #drop redundant cols
#merge CC_8, CC_5 and CC_30 together
dat3 <- merge_CCs(dat3,"CC_8_")
dat3 <- merge_CCs(dat3,"CC_30_")
dat3 <- merge_CCs(dat3,"CC_5_")

#clean up names and reorder
names(dat3)[names(dat3) == "MLST_93"] <- "CC_93"
dat3 <- dat3[,mixedsort(colnames(dat3))]
colnames(dat3) <- gsub("(CC_.{0,3})_.{0,4}$","\\1",colnames(dat3))
#remove missing samples
missing_samples <- c("SRS021960","SRS098620") #data consistency issue with these samples
dat4 <- filter(dat3,!(Sample.Id %in% missing_samples))


combined <- inner_join(mapping,dat4,by = c("Sample_id" = "Sample.Id"))
#remove duplicated records
combined <- combined[-c(46,95,96),]
colnames(combined)[which(colnames(combined) == "Body_Site")] <-  "Body.site"
colnames(combined)[which(colnames(combined) == "Sample_id")]  <- "Sample.Id"
combined$Body.site <- as.factor(combined$Body.site)
combined$Subject.Id <- as.factor(combined$Subject.Id)
```
#plot unflitered coverage

```{r}
with(mapping, plot(Staph_cov,mecA_cov, log = "x", xlim=c(0.01,20), ylim=c(0,10), ylab = "mecA coverage", xlab = "log(Staph. coverage)", pch = 16))

```


###Filter at two levels of Staph coverage and write files
```{r}
cov0.025 <- filter(combined, Staph_cov > 0.025)
cov0.5 <- filter(combined, Staph_cov > 0.5)
write.table(cov0.025,"./Data/cov0.025")
write.table(cov0.5,"./Data/cov0.5")
write.table(combined,"./Data/combined")
cat("Number of samples above cov > 0.025 threshold = ",nrow(cov0.025))
cat("Number of samples above cov > 0.5 threshold = ",nrow(cov0.5))
```

###For cov > 0.025 plot the coverage at different body sites and other relationships

```{r}
plot_coverages(cov0.025, "Cov. > 0.025 by body site")
plot_adjusted_coverages(cov0.025, "Adjusted covs by subtype: floor = 0.025")
plot_mecA(cov0.025,"Cov > 0.025 versus mecA , colored by body site")
plot_diversity_vers_cov(cov0.025,"Shannon diversity of calls versus coverage: cutoff cov > 0.025")
```

###Same plots for cov > 0.5 pl
```{r}
plot_coverages(cov0.5, "Cov. > 0.5 by body site")
plot_adjusted_coverages(cov0.5, "Adjusted covs by subtype: floor = 0.5")
plot_mecA(cov0.5,"Cov > 0.5 versus mecA , colored by body site")
plot_diversity_vers_cov(cov0.5,"Shannon diversity of calls versus coverage: cutoff cov > 0.5")
```

###Same plots for all data
```{r}
plot_coverages(combined, "coverage by body site")
plot_adjusted_coverages(combined, "Adjusted covs by subtype")
plot_mecA(combined,"Staph coverage versus mecA , colored by body site")
plot_diversity_vers_cov(combined,"Shannon diversity of calls versus coverage")
```

###Session info
```{r}
sessionInfo()
```
