---
title: "Rare SNP analysis on HMP filtered at 0.5x coverage"
author: "Tim Read"
date: "August 14, 2015"
output: html_document
---

##Rare SNPs on 0.025x filtered HMP data
Pipeline is a bit messy but should be OK for now. Originally developed in HMP_cooccuance.R.

```{r}
library(reshape2)
library(dplyr)
library(gdata)
library(gtools)
source('./staph_metagenome_tools.R')
```

Read in the datframe from the HMP coverage analysis

```{r}
dat4 <- read.table("./Data/cov0.5")
#dat4 has no meaning, just a temporary name 
```

Create co-occurence table 
```{r}
#analysis of rare snps
multiSubjects <- count(dat4,Subject.Id) %>% filter(n > 1) %>% select(Subject.Id )
dat <- read.table("./Data/med_freq_snps.table", header = FALSE)
dat <- filter(dat,V2 %in% dat4$Sample.Id)
u <- create_cooccur_mat(dat) #slooow
u.hits <- calc_hits(colnames(u),u)
```

Rest of the pipeline.  Bit of a mess but it provides results.
### co-occurrence of rare SNPs within body sites
```{r}

bs <- levels(dat4$Body.site)
for (i in bs) {
      bss_rows <- which(dat4$Body.site == i)
      if (length(bss_rows) > 3) {
      bss_samples <- slice(dat4,bss_rows)$Sample.Id %>% as.character()
      u.subset <- which(colnames(u) %in% bss_samples)
      print(i)
      FM_res <- calc_FTS(u.hits,calc_hits(bss_samples,u))
      print(FM_res)
      cat("\n")
    }
    else {
      cat("Less than 4 samples in ", i, "\n\n")
      }
  }


```
### Fisher test for enrichment of rare SNPs within different body sites of the same subjects
```{r}
sub.hits = 0
sub.nohits = 0
for (i in multiSubjects$Subject.Id) {
  sub <- filter(dat4, Subject.Id == as.character(i))$Sample.Id %>% as.character()
  #missing expression
  subres <- calc_hits(sub,u)
  sub.hits <- subres[1] + sub.hits
  sub.nohits <- subres[2] + sub.nohits
}
calc_FTS(u.hits,c(sub.hits,sub.nohits))



```
### rare SNP enrichment between specific pairs of sites
```{r}
###At the moment I need to carefully test and debug the function that produces the matrix.  Discounting for now
multiBodySite <- count(dat4,Body.site) %>% filter(n > 8) %>% select(Body.site)
lmbs <- levels(multiBodySite$Body.site)
pers <- combinations(length(lmbs),2,lmbs)
for (i in 1:(nrow(pers))) {
  print(intra_body_FTS(pers[i,1],pers[i,2],dat4,multiSubjects,u))
}

```


###Session info
```{r}
sessionInfo()
```

